Unbiased pangenome graphs

### 2022-02-10 manuscript/fig_experiments.tex
l/m swap in the pseudocode and tweaks

\begin{figure}[b]
%  \centering
   \includegraphics[width=\linewidth]{fig_experiment_stats.pdf}
   \caption{
     Experimental results from the application of \textit{seqwish} to four different pangenomes.
     Multiple minimum identity settings for the mapping (\textit{wfmash -p}) and different minimum match length filter settings result in a collection of graph builds per pangenome input.
     We compare the runtime in hours with the size of the resulting graphs relative to the average size of an input genome in the particular set.
     Lower limits on pairwise identity result in more compact graphs.
     Similarly, filtering short matches increases graph size relative to not (\textit{seqwish -k}=0, red).
     Increasing the \textit{seqwish -k} parameter tends to increase the size of the graph.
    }
    \label{fig:experiments}
\end{figure}

>>>>

\begin{figure}[b]
%  \centering
   \includegraphics[width=\linewidth, trim=0.4cm 0cm 0.4cm 1cm]{fig_experiment_stats}
   \caption{
     Experimental results from the application of \textit{seqwish} to four different pangenomes.
     Multiple minimum identity settings for the mapping (\textit{wfmash -p}) and different minimum match length filter settings (\textit{seqwish -k}) result in a collection of graph builds per pangenome input.
     We compare the runtime in hours with the size of the resulting graphs relative to the average size of an input genome in the particular set.
     Lower limits on pairwise identity result in more compact graphs.
     Similarly, filtering short matches increases graph size relative to not (\textit{seqwish -k}=0, red).
     The other way around, increasing the \textit{seqwish -k} parameter tends to increase the size of the graph.
    }
    \label{fig:experiments}
\end{figure}

### 2022-02-10 manuscript/main.tex
l/m swap in the pseudocode and tweaks

\begin{table*}[!ht]
    \centering
    \caption{Performance of the graph induction algorithm.
        For each pangenome we have chosen a single experiment with the given \textit{seqwish -k} filter setting of 49bp.
        }
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
        \hline
        species & sequences & haplotypes & fasta.Gbps & min.match.bp & time.seconds & memory.Gbytes & disk.Gbytes & graph.Gbps & components \\ \hline
        \textit{A. thaliana} & 922 & 16 & 1.90251 & 49 & 468 & 43.1287 & 7.1218 & 0.234284 & 100 \\ \hline
        \textit{H. sapiens} & 17478 & 38 & 114.627 & 49 & 46268 & 347.4983 & 604.4261 & 4.47126 & 474 \\ \hline
        \textit{H. pylori} & 292 & 250 & 0.407782 & 49 & 790 & 75.7514 & 20.2070 & 0.01421 & 5 \\ \hline
        \textit{Z. mays} & 46289 & 41 & 90.2491 & 49 & 31043 & 351.1235 & 402.8716 & 13.8838 & 925 \\ \hline
    \end{tabular}
\end{table*}

@@

Code and links to data resources used to build this manuscript and its figures, can be found in the paper's public repository: \url{https://github.com/pangenome/seqwish-paper}.

>>>>

\begin{table*}[!ht]
    \centering
    \caption{Performance of the graph induction algorithm.
        For each pangenome we report a single experiment with the given \textit{seqwish -k} filter setting of 49bp.
        }
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
        \hline
        species & sequences & haplotypes & fasta.Gbps & min.match.bp & time.seconds & memory.Gbytes & disk.Gbytes & graph.Gbps & components \\ \hline
        \textit{A. thaliana} & 922 & 16 & 1.90251 & 49 & 468 & 43.1287 & 7.1218 & 0.234284 & 100 \\ \hline
        \textit{H. sapiens} & 17478 & 38 & 114.627 & 49 & 46268 & 347.4983 & 604.4261 & 4.47126 & 474 \\ \hline
        \textit{H. pylori} & 292 & 250 & 0.407782 & 49 & 790 & 75.7514 & 20.2070 & 0.01421 & 5 \\ \hline
        \textit{Z. mays} & 46289 & 41 & 90.2491 & 49 & 31043 & 351.1235 & 402.8716 & 13.8838 & 925 \\ \hline
    \end{tabular}
\end{table*}

@@

Code and links to data resources used to build this manuscript and its figures can be found in the paper's public repository: \url{https://github.com/pangenome/seqwish-paper}.
